---
title: "Initial Data Exploration Report"
date: "`r format(Sys.time(), '%d %B, %Y')`"
author: "Grant Holtes"
output:
  rmarkdown::html_document:
    theme: yeti
params:
  data: data
---

```{r setup, include=FALSE}
###Load files###
library(knitr)
source("univarient.R")
source("bivarient.R")
knitr::opts_chunk$set(echo = TRUE)

###read params###
dt <- params$data
filename = "params$data"
```

## Summary

### Data file information
High level summary of the data file and available variables.

```{r, echo=FALSE}
kable(data_table_summary(dt, filename))
```

Note that numeric data may be any one of `double, integer, complex, logical or numeric`

### Variable Details
Information on each available variable.
```{r, echo=FALSE}
kable(univarient_table_summary(dt))
```

## Distributions of variables

### Numeric distributions
Understanding the distribution of numeric data is useful for informing data cleaning and modelling. Numeric data is assumed to be continuous for the creation of these distributions.

```{r, echo=FALSE, message=FALSE, warning = FALSE}
distributions(dt)
```

### Categorical distributions
Categorical data is explored through the frequencies of occurrence of each category.
```{r, echo=FALSE, message=FALSE, warning = FALSE}
hists(dt)
```

## Correlations between variables


### Correlation Matrix
Linear correlation between variables, yields values between 1, -1. 1 and -1 correspond to perfect positive and negative relationships respectively, while values close to zero suggest no relationship between the variable pair. 
```{r, echo=FALSE, message=FALSE, warning = FALSE}
corrMat(dt)
```

### Pairwise Matrix
Scatter plots for each pair of variables.
```{r, echo=FALSE, message=FALSE, warning = FALSE}
PairScatter(dt)
```

### Regressions
Scatter plots and regressions for the three strongest pairwise correlations.
```{r, echo=FALSE, message=FALSE, warning = FALSE}
regressions(dt)
```
